---
title: "Alcohol vs Seat choice"
author: "Angelica Lopez- Esparza"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```  

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```  

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
library(ggplot2)

# Create a notched boxplot with red outliers and centered, bold title
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box Plot By Seat") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


```

use chat Gpt to create a code for a notched boxplot.   


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
``` 
  average is the same as mean, the mean amount of alc that theyre drinking in the back is 9.6 drinks, in the front its 1.8 and in the middle is 3.2. the back rows are drinking more than the rows in front of them. the average amount of drinks in the back is larger than the front or middle. most people are sitting inthe middle row while the least amount of people are sitting in the back.   
    
    
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```
the difference between the front and the back is drinks is the confidence interval. zero crosses the confidence interval which tells us that the front and the middles have no differences. the back is different from the front and th back is different front the middle but the middle and the front have no difference, there is a difference between the back row and the other two rows.  


## Conclusions
We used Chat GPT to create a notch plot that told us the alcohol consumption difference compared to the row seats. we committed and pushed. we copied a code from our numerical~catrmd cheat file adn pasted that to get our numerical table, then we summarized that. we copied another code from the same cheat sheet file and pasted that in to run our ttest, afterwards we ran something called tukeyHSD to help us determine the difference between the rows because the ttest wasn't as clear in telling us the differences. we summarized and played with chat gpt to create an anova result. 
